\textsc{Remarks on the vanishing viscosity process of state-constraint Hamilton--Jacobi equations}

### 2021-07-15 Drafts and notes/Draft_05.tex
Almost final

\begin{rem} To the best of our knowledge, this theorem is new in the literature. We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation. The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows. One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}). If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain. Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
\begin{equation}\label{heur1}
    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
\end{equation}
and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$. After taking derivative, heuristically, \eqref{heur1} becomes
\begin{equation}\label{heur2}
    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
\end{equation}
This suggests that $Du^\varepsilon \approx \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}$. We show that this is indeed true (Lemma \ref{lem:boundDu^eps}).

\textcolor{blue}{
However, to get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$. It turns out that such an estimate is quite delicate. We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
\end{rem}

@@

\subsection{Local gradient estimate} 
The following theorem is about the local gradient bound as in \cite[Appendix]{Lasry1989}. The technique being used is the classical Bernstein method. Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$.

\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u^\varepsilon \in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u^\varepsilon] = 0$ in $\Omega$. Let $m:= \max_{\overline{\Omega}}f(x)$. Then for $\delta>0$, there exists $C_\delta = C(m,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that 
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \Big(|u^\varepsilon(x)|+|Du^\varepsilon(x)|\Big) \leq C_\delta
\end{equation*}
for $\varepsilon$ small enough.
\end{thm}
%\textcolor{orange}{(I think here we want to add for $\varepsilon$ small enough?)}

\noindent A proof of this theorem is provided in Appendix for the reader's convenience.

@@

\begin{thm}[Constant data]\label{thm:rate_doubling0} Assume $f\equiv C_f$ in $\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv C_f$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ such that 
    \begin{equation*}
    \begin{split}
    &0\leq u^\varepsilon(x) - u(x)\leq C \left(\frac{ \varepsilon^{\alpha+1}}{d(x)^\alpha} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right),  \qquad\qquad \;\;\; \text{if}\; 1<p<2,\\
    &0\leq u^\varepsilon(x) - u(x)\leq C \left(\varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right) + \frac{\varepsilon^{2}}{\delta_{0,\Omega}^{2}}\right),  \qquad \text{if}\; p=2,
    \end{split}
\end{equation*}
for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}. In particular, if $1<p<2$ then
\begin{equation*}
    C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon, \qquad x\in \Omega_\varepsilon.
\end{equation*}
Furthermore, for all $1<p\leq 2$ there holds $|u^\varepsilon-C_f| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
\end{thm}
%\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
\begin{proof} Lemma \ref{lem:f=0} implies $u \equiv C_f$ in $\Omega$. And Lemma \ref{lem:lower-bound} tells us $u^\varepsilon-u=u^\varepsilon-C_f \geq 0$.By the comparison principle of \eqref{eq:PDEeps} and Lemma \ref{lem:super_refined}, the conclusion follows.
\end{proof}

@@

where $C_\frac{\kappa}{2}$ is the upper bound of $Du^\varepsilon$ in $\Omega_\frac{\kappa}{2}$, as is given in the a priori estimate (Theorem \ref{thm:grad_1}) and $C$ is a constant that depends only on $\nu$, $\alpha$, and bounds on $d,Dd$ and $\Delta d$. Using \eqref{delta_psi} and \eqref{convex4} in \eqref{convex3}, we get

@@

\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, we need to know more about the blow up rate $C_\kappa$ in $|Du^\varepsilon(x)|\leq C_\kappa$ as $\kappa\to 0$. We will use the result in

\end{rem}

\begin{cor} Assume $f = 0$ on $\partial\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Let $K$ be a compact subset of $\Omega$, then there exists a constant $C_K$ such that 
\begin{equation*}
    \sup_{x\in K} \big(u^\varepsilon(x) -u(x)\big) \leq C_K\varepsilon.
\end{equation*}
\end{cor}
\begin{proof} We can find $\kappa\in \left(0,\delta_0\right)$ such that $K\subset\subset \Omega_{\kappa}$. Define $f_\kappa$ as in the proof of Theorem \ref{main_thm1}, where $\mathrm{supp}(f_\kappa)\subset\Omega_{\frac{\kappa}{2}}$ and
\begin{equation*}
    0\leq f - f_\kappa \leq L\kappa
\end{equation*}
where $L$ is the Lipschitz constant of $f$. Let $u^\varepsilon_\kappa\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the solution to \eqref{eq:PDEeps} with datum $f_k$ and $u_k$ be the solution to \eqref{eq:PDE0} with datum $f_k$, then
\begin{equation*}
  0\leq u^\varepsilon(x) - u^\varepsilon_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega
\end{equation*}
and
\begin{equation*}
    0\leq u(x) - u_\kappa(x)\leq L\kappa \qquad\text{for}\;x\in \Omega.
\end{equation*}
Therefore
\begin{equation*}
    u^\varepsilon(x)-u(x)\leq 2L\kappa + \big(u^\varepsilon_\kappa - u_\kappa\big) \leq 2L\kappa+C_{\kappa}\varepsilon
\end{equation*}
where we use the rate $\mathcal{O}(\varepsilon)$ from Theorem \ref{thm:rate_doubling2} as $f_\kappa$ is compactly supported. 
\end{proof}

\begin{rem} It is clear from the proof that $C_K$ blows up as $K$ approaching $\Omega$ and we do not have any boundary layer yet, since the bound $|Du^\varepsilon(x)|\leq C_\kappa$ for $x\in \Omega_\kappa$ is not an explicit bound. We refer the readers to \cite{alessio_asymptotic_2006} for an explicit behavior of $Du^\varepsilon(x)$ as $x\to \partial \Omega$. Of course, using this explicit behavior of $Du^\varepsilon$ we can obtain a boundary layer from this proof, which we omit it here.
\end{rem}

\begin{proof}[Proof of Theorem \ref{main_thm2}] Define

>>>>

\begin{rem} To the best of our knowledge, this theorem is new in the literature. We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation. The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows. One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}). If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain. Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
\begin{equation}\label{heur1}
    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
\end{equation}
and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$. After taking derivative, heuristically, \eqref{heur1} becomes
\begin{equation}\label{heur2}
    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
\end{equation}
\textcolor{blue}{
To get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$. It turns out that such an estimate is quite delicate. We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
\end{rem}

@@

\subsection{Local gradient estimate} Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$. We state a priori estimate for $\rmC^2$ solutions of \eqref{eq:PDEeps} (\cite[Appendix]{Lasry1989}). Since we are working with nice solutions, the proof is relatively simple using the classical Bernstein method (\cite{bernstein_sur_1910}). We provide a proof in Appendix for the readers' convenience.

\begin{thm}\label{thm:grad_1} Let $f\in \rmC(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $u^\varepsilon \in \mathrm{C}^2(\Omega)$ be a solution to $\mathcal{L}^\varepsilon[u^\varepsilon] = 0$ in $\Omega$. Let $m:= \max_{\overline{\Omega}}f(x)$. Then for $\delta>0$, there exists $C_\delta = C(m,p,\delta, \Vert D f\Vert_{L^\infty(\Omega)})$ such that 
\begin{equation*}
    \sup_{x\in \overline{\Omega}_\delta} \Big(|u^\varepsilon(x)|+|Du^\varepsilon(x)|\Big) \leq C_\delta
\end{equation*}
for $\varepsilon$ small enough.
\end{thm}

%\textcolor{orange}{(I think here we want to add for $\varepsilon$ small enough?)}

@@

\begin{thm}[Constant data]\label{thm:rate_doubling0} Assume $f\equiv C_f$ in $\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u \equiv C_f$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ such that 
    \begin{equation*}
    \begin{split}
    &0\leq u^\varepsilon(x) - u(x)\leq C \left(\frac{ \varepsilon^{\alpha+1}}{d(x)^\alpha} + \frac{\varepsilon^{\alpha+2}}{\delta_{0,\Omega}^{\alpha+2}}\right),  \qquad\qquad \;\;\; \text{if}\; 1<p<2,\\
    &0\leq u^\varepsilon(x) - u(x)\leq C \left(\varepsilon \mathrm{log}\left(\frac{1}{d(x)}\right) + \frac{\varepsilon^{2}}{\delta_{0,\Omega}^{2}}\right),  \qquad \text{if}\; p=2,
    \end{split}
\end{equation*}
for $x\in \Omega$, where $\delta_{0,\Omega}$ is defined as in \eqref{def:delta_0}. In particular, if $1<p<2$, we have $C_f\leq u^\varepsilon(x)\leq C_f + C\varepsilon$ for $x\in \Omega_\varepsilon$ and $|u^\varepsilon(x)| = \mathcal{O}\left(\varepsilon^{\alpha+1}\right)$ on each compact subset of $\Omega$.
\end{thm}
%\textcolor{orange}{(Did you mean "In particular $0\leq  u^\varepsilon(x) \leq C\varepsilon$ for $x\in \Omega_\varepsilon$" ?)}
\begin{proof} Lemma \ref{lem:f=0} implies $u \equiv C_f$ in $\Omega$. And Lemma \ref{lem:lower-bound} tells us $u^\varepsilon-u=u^\varepsilon-C_f \geq 0$.By the comparison principle of \eqref{eq:PDEeps} and Lemma \ref{lem:super_refined}, the conclusion follows.
\end{proof}

@@

where, as is given in the a priori estimate (Theorem \ref{thm:grad_1}),
\begin{equation}\label{est_Ckappa}
    |Du^\varepsilon(x)|\leq C_{\frac{\kappa}{2}}, \qquad \;x\in \Omega_{\frac{\kappa}{2}},
and $C$ is a constant that depends only on $\nu$, $\alpha$, and bounds on $d,Dd$ and $\Delta d$. Using \eqref{delta_psi} and \eqref{convex4} in \eqref{convex3}, we get

@@

\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, it is necessary to know explicitly how the constant $C_\kappa$ in \eqref{est_Ckappa} blows up as $\kappa\to 0$. Fortunately, such a refined version of the local gradient bound is available, for instance \cite[Theorem 3.1]{Armstrong2015} where the authors use Bernstein's method inside a doubling variables argument and explicitly keeping track of all dependencies. We refer the readers to \cite{armstrong_stochastic_2012, barles_weak_1991,capuzzo_dolcetta_holder_2010} and the references therein for related versions of the gradient bound.
\end{rem}

\begin{lem} There exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
|Du^\varepsilon(x)| \leq C\left( 1 + \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}\right) \qquad\text{for}\;x\in \Omega.
\end{equation*}
\end{lem}

\begin{rem} Using our approach, in order to relax the assumption $\mathrm{supp}(f)\subset\subset\Omega$ to $f = 0$ on $\partial\Omega$ as in Theorem \ref{main_thm1}, we need to know more about the blow up rate $C_\kappa$ in $|Du^\varepsilon(x)|\leq C_\kappa$ as $\kappa\to 0$. Here are some results in the literature: if $u$ solves ($f\in \mathrm{C}^1(\overline{\Omega}), f\geq 0$)
\begin{equation*}
\begin{cases}
    \lambda u + |Du|^p - f(x) - \Delta u = 0&\qquad\text{in}\;\Omega,\\
    u = +\infty&\qquad\text{on}\;\partial\Omega
\end{cases}
\end{equation*}
then we can have a better bound in a priori estimate (\cite{lions_quelques_1985}) 
\begin{equation*}
    |Du(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
\end{equation*}
where $\alpha = \frac{2-p}{p-1}$, while (\cite{alessio_asymptotic_2006}) gives an asymptotic behavior
\begin{equation*}
    \lim_{d(x)\to 0} \Big(Du(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0).
\end{equation*}
Here $\underline{x}$ is the unique projection of $x$ (near the boundary) onto $\partial\Omega$ and $\mathfrak{n}(x_0)$ is the unit outward normal vector of $\Omega$ at $x_0$. 
\paragraph{\textbf{Our version with $\varepsilon$}}
In our version, the problem with $\varepsilon$, we have 
\begin{equation*}
\begin{cases}
    \lambda u^\varepsilon + |Du^\varepsilon|^p - f(x) - \varepsilon\Delta u^\varepsilon = 0&\qquad\text{in}\;\Omega,\\
    u^\varepsilon = +\infty&\qquad\text{on}\;\partial\Omega
\end{cases}
\end{equation*}
we can obtain that
\begin{equation}\label{eq:yy}
    |Du^\varepsilon(x)| \leq \frac{C}{d(x)^{\alpha+1}}, \qquad x\in \Omega
\end{equation}
and 
\begin{equation}\label{eq:xx}
    \lim_{d(x)\to 0} \Big(Du^\varepsilon(x)\cdot Dd(x)\Big)d(x)^{\alpha+1} = (\alpha+1)^{\alpha+1}\mathfrak{n}(x_0)\varepsilon^{\alpha+1}.
\end{equation}

\paragraph{\textbf{The result that we need for Theorem \ref{main_thm2}}} The ideal estimate we are expecting is, there exists a constant $C$ independent of $\varepsilon$ such that
\begin{equation*}
|Du^\varepsilon(x)| \leq C + \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha+1}} \qquad\text{for}\;x\in \Omega.
\end{equation*}
This estimate can be proven following from a priori estimate $|Du^\varepsilon(x)|\leq C_\delta$ for $x\in \Omega_\delta$ and \eqref{eq:xx} if the limit in \eqref{eq:xx} is uniform in $\varepsilon$.

\paragraph{\textbf{Difficulty}} However, \eqref{eq:xx} is not uniform in $\varepsilon$ (at least from the method the authors Porretta and Veron use in \cite{alessio_asymptotic_2006}).
\end{rem}

%\begin{proof}[Proof of Theorem \ref{main_thm2}] Define

%\end{proof}
